### 2017-03-29 thesis/thesis.tex
finished editing up to the discussion
tmp commit
debugged the blank page before acronyms - tmp commit
pretty much ready to submit - tmp commit

% Preamble:
\usepackage[T1]{fontenc}                            % package for specifying output font encoding
\usepackage[acronym,style=super]{glossaries}                    % package for making glossaries
\usepackage[flushleft]{threeparttablex}             % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption} % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}        % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                           % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}          % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                          % package for making appendices
\usepackage[utf8]{inputenc}                         % package for specifying input font encoding
\usepackage{chngcntr}                               % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                               % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                               % package for Times New Roman font
\usepackage{natbib}                                 % package for reference management
\usepackage{setspace}                               % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                        % package for making colours
\usepackage{booktabs}                               % package for better looking tables
\usepackage{longtable}                              % package for tables that span multiple pages
\usepackage{siunitx}                                % package for scientific notations and units
\usepackage{etoolbox}                               % package to 'robustify' \bfseries

@@

% Change the title of Table of Contents:
\renewcommand{\thesubfigure}{\Alph{subfigure}}

@@

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
% \includeonly{{./intro/intro}}
% \includeonly{{./methods/methods}}
\includeonly{{./results/results2},{./discussion/discussion},{./misc/appendix},{./misc/appendix2}}
% \includeonly{{./results/results}}
% \includeonly{{./results/results2}}
% \includeonly{{./discussion/discussion}}
% \includeonly{{./misc/appendix}}
% \includeonly{{./misc/appendix2}}

@@

@@

>>>>

% Preamble:
\usepackage[T1]{fontenc}                                 % package for specifying output font encoding
\usepackage[acronym,style=super,nogroupskip,section=chapter]{glossaries} % package for making glossaries
\usepackage[flushleft]{threeparttablex}                  % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption}      % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}             % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                                % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}               % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                               % package for making appendices
\usepackage[utf8]{inputenc}                              % package for specifying input font encoding
\usepackage{chngcntr}                                    % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                                    % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                                    % package for Times New Roman font
\usepackage{natbib}                                      % package for reference management
\usepackage{setspace}                                    % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                             % package for making colours
\usepackage{booktabs}                                    % package for better looking tables
\usepackage{longtable}                                   % package for tables that span multiple pages
\usepackage{siunitx}                                     % package for scientific notations and units
\usepackage{etoolbox}                                    % package to 'robustify' \bfseries

@@

% Change the title of Table of Contents:
% \renewcommand{\thesubfigure}{\Alph{subfigure}}

@@

% Remove unnecessary spaces between the figures from different chapters in LoF and LoT:
\newcommand*{\noaddvspace}{\renewcommand*{\addvspace}[1]{}}
\addtocontents{lof}{\protect\noaddvspace}
\addtocontents{lot}{\protect\noaddvspace}

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
% \includeonly{{./misc/title},{./misc/abstract},{./misc/acknowledgement},{./methods/methods},{./intro/intro},{./results/results},{./results/results2},{./discussion/discussion}}
\includeonly{{./misc/title},{./misc/abstract},{./misc/acknowledgement}}
% \includeonly{{./intro/intro}}
% \includeonly{{./methods/methods}}
% \includeonly{{./results/results2},{./discussion/discussion},{./misc/appendix},{./misc/appendix2}}
% \includeonly{{./results/results}}
% \includeonly{{./results/results2}}
% \includeonly{{./discussion/discussion}}
% \includeonly{{./misc/appendix}}
% \includeonly{{./misc/appendix2}}

@@

% Need to set line spacing to single space, otherwise it inserts a blank page for an unknown reason:
\singlespacing

@@

% Reset the spacing to 1.5:
\onehalfspacing
